Synthesizing Quotient Lenses

### 2018-03-09 papers/QuotientLenses/main.tex
Checkpoint

We have implemented QREs and the quotient lens synthesis algorithm described
above as an extension to the Boomerang interpreter~\cite{Boomerang}. Thanks to this integration, QREs and quotient lens
synthesis tasks can now be expressed alongside existing Boomerang terms, and we
can combine the two kinds of lenses seamlessly in the same application.
Intuition suggests that the increased expressiveness of QREs should make many
lens programming tasks easier, but we would like more quantitative understanding
of that claim.  We thus conducted several experiments that aim to provide
answers to the following questions:

\begin{enumerate}
  \item Does synthesizing quotient lenses from QREs permit an easier development
  process than existing approaches?

  \item Does the increase in expressivity gained from synthesizing from QREs
  permit synthesis of more useful lenses than existing approaches.

  \item Does our tool synthesize lenses fast enough to be used as part of a
  standard development process.
\end{enumerate}

@@

\item The remaining eight benchmarks were derived from
  data.gov.\footnote{\url{http://data.gov}} These datasets include census
  population data, wage comparison data, demographics statistics data and
  crime index data. We chose these datasets since they were stored in XML, CSV
  and RDF formats which are more easily specified using regular expressions than
  plain text or PDF documents.
\end{enumerate}

@@

The value of \CanonizerAndSpecSize{} estimates the burden for writing our
benchmarks within the Optician system, without QREs but still using
synthesis. This is only an approximation, as both $W(q_1)$ and $\canonizer(q_1)$ are
automatically generated from the QRE, and it is possible that a human-written
version might be smaller.

The value of \LensAndSpecSize{} estimates the burden in writing our benchmarks
in Boomerang, using neither QREs nor synthesis. This value is also an
approximation, as $W(q_1)$ and $\canonizer(q_1)$ and the bijective lens are all
automatically generated.

>>>>

We have implemented QREs and the quotient lens synthesis algorithm described
above as an extension to the Boomerang interpreter~\cite{boomerang,quotientlenses}. Thanks to this integration, QREs and quotient lens
synthesis tasks can now be expressed alongside existing Boomerang
terms\bcp{what's the difference between a task and a term (and how do each
  of them relate to ``lenses'' just below)?}, and we
can combine the two kinds of lenses seamlessly in the same application.
Intuition suggests that the increased expressiveness of QREs should make many
lens programming tasks easier, but we would like more quantitative understanding
of that claim.  We thus conducted several experiments that aim to provide
answers to the following questions:

\begin{enumerate}
  \item Does synthesizing quotient lenses from QREs permit an easier development
  process than existing approaches?  \bcp{Needlessly vague: What existing approaches?  Writing
  them by hand?}

  \item Does the increase in expressivity gained from synthesizing from QREs
  permit synthesis of more useful lenses than existing approaches.  \bcp{Is
    this really an interesting empirical question?  Seems obvious, from the
    arguments we made in Section 2 and the intro.}

  \item Does our tool synthesize lenses fast enough to be used as part of a
  standard development process.  \bcp{Should there be some question marks
    around here.}
\end{enumerate}

@@

\item The remaining eight benchmarks were derived from datasets found at 
  data.gov. These datasets include census
  population data, wage comparison data, demographics statistics data and
  crime index data. We chose these datasets since they were stored in XML, CSV
  and RDF formats which are more easily specified using regular expressions than
  plain text or PDF documents.  \bcp{Why did we include these eight new
    ones?  Are they significantly different (more complex, exercising
    different features of the synthesis algorithm or QRE syntax, ...)?}
\end{enumerate}

@@

The value of \CanonizerAndSpecSize{} estimates the burden for writing our
benchmarks within the Optician system, without QREs but still using
synthesis. (This is only an approximation, as both $W(q_1)$ and $\canonizer(q_1)$ are
automatically generated from the QRE, and it is possible that a human-written
version might be smaller.)

The value of \LensAndSpecSize{} estimates the burden in writing our benchmarks
in Boomerang, using neither QREs nor synthesis. (This is also an
approximation, as $W(q_1)$ and $\canonizer(q_1)$ and the bijective lens are all
automatically generated.)
